{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2015-01-28 brains-protocol.tex
Dots for decimal numbers, not commas

\begin{quote}
    ``The massive economic upheaval being experienced across the globe is sparing no one in the consumer electronics world.''
\end{quote}
and a smaller number of media websites, and blogs, reported the following,
\begin{quote}
    ``The massive economic upheaval being experienced across the \textbf{world} is sparing no one in the consumer electronics world.''
\end{quote}
The word \emph{globe} is acquired at an average of 6,5 years old, appears about 3,5k times in the dataset, and has a Clustering coefficient of 0,24.
The word it was replaced with, \emph{world}, is acquired on average at 5,3 years old, appears about 146k times in the dataset, and has a Clustering coefficient of 0,05. (Both words have four phonemes.)
Such a change, though minor in appearance, is a typical example of alteration along the lines shown by our results.

>>>>

\begin{quote}
    ``The massive economic upheaval being experienced across the globe is sparing no one in the consumer electronics world.''
\end{quote}
and a smaller number of media websites, and blogs, reported the following,
\begin{quote}
    ``The massive economic upheaval being experienced across the \textbf{world} is sparing no one in the consumer electronics world.''
\end{quote}
The word \emph{globe} is acquired at an average of 6.5 years old, appears about 3.5k times in the dataset, and has a Clustering coefficient of 0.24.
The word it was replaced with, \emph{world}, is acquired on average at 5.3 years old, appears about 146k times in the dataset, and has a Clustering coefficient of 0.05. (Both words have four phonemes.)
Such a change, though minor in appearance, is a typical example of alteration along the lines shown by our results.
